---
title: "ggplot_hook"
author: "Huong Vo"
date: "10/31/2021"
output: html_document
---
## Setting up my environment
Notes: Setting up my R environment by loading the "tidyverse" and "palmerpenguins" packages
```{r loading packages}
library(tidyverse)
library(palmerpenguins)
```

## Visualizations
Here we will go through a series of visualizations

### Flipper length and body mass in purple
Here, we will plot flipper length against body mass
```{r visualize flipper length and body mass in purple}
ggplot(data = penguins)+
  geom_point(mapping = aes(x = flipper_length_mm,y = body_mass_g),color = "purple")
```

### FLipper length and body mass by species
Here, we plot flipper lengtha against body mass and look at the breakdown by species
```{r species}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = flipper_length_mm,y = body_mass_g,color = species))
```

### Flipper length and body mass by species and sex
Here, we plot flipper length against body mass and look at the breakdown by species and sex
```{r species and sex}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = flipper_length_mm,y = body_mass_g,color = species,shape = species))+
  facet_wrap(~sex)

```

